---
title: "10 Years of Historical Price 01/09/2008 ~ 01/09/2018"
output:
  word_document: default
  html_notebook: default
---

SECTION 0 - OBTAIN AND TRANSFORMING DATA

3M CSV dataset

```{r}
dataset_MMM <- read.csv("MMM.csv")
head(dataset_MMM)
summary(dataset_MMM)
```

C CSV dataset
```{r}
dataset_C <- read.csv("C.csv")
head(dataset_C)
summary(dataset_C)
```

PG CSV dataset
```{r}
dataset_PG <- read.csv("PG.csv")
head(dataset_PG)
summary(dataset_PG)
```

GOOG CSV dataset
```{r}
dataset_GOOG <- read.csv("GOOG.csv")
head(dataset_GOOG)
summary(dataset_GOOG)
```

MYL CSV dataset
```{r}
dataset_MYL <- read.csv("MYL.csv")
head(dataset_MYL)
summary(dataset_MYL)
```


Retrieve the daily closing price
```{r}
# Initialize date column for analyze purpose
close_price = NULL
close_price$date = dataset_MMM$Date

close_price$MMM = dataset_MMM$Adj.Close
close_price$C = dataset_C$Adj.Close
close_price$PG = dataset_PG$Adj.Close
close_price$GOOG = dataset_GOOG$Adj.Close
close_price$MYL = dataset_MYL$Adj.Close

#Show several example of each asset's close price
head(close_price$MMM)
head(close_price$C)
head(close_price$PG)
head(close_price$GOOG)
head(close_price$MYL)
```

Construct the log daily returns of each asset
```{r}
# Initialize date column for analyze purpose
returns = NULL
returns$MMM = diff(log(close_price$MMM), lag = 1)
returns$C = diff(log(close_price$C), lag = 1)
returns$PG = diff(log(close_price$PG), lag = 1)
returns$GOOG = diff(log(close_price$GOOG), lag = 1)
returns$MYL = diff(log(close_price$MYL), lag = 1)

#Show several example of each asset's close price
head(returns$MMM)
head(returns$C)
head(returns$PG)
head(returns$GOOG)
head(returns$MYL)
```

Insert the result into data frame format
```{r}
transformed_data.close <- data.frame(close_price$date, close_price$MMM, close_price$C, close_price$PG, close_price$GOOG, close_price$MYL)
str(transformed_data.close)

n <- nrow(transformed_data.close)

returns$date <- close_price$date[2:n]

transformed_data.returns <- data.frame(returns$date, returns$MMM, returns$C, returns$PG, returns$GOOG, returns$MYL)
str(transformed_data.returns)
```


SECTION 1 - EXPLORATORY DATA ANALYSIS

Generate a time plot series of closing price on the same graph
```{r}
# Load necessary packages
library(tidyverse)
library(ggplot2)


# View time plot of the closing price
 ggplot(data = transformed_data.close, 
        aes(x=as.Date(close_price$date), y=value, group=1) ) + 
        geom_line(aes(y=close_price$MMM, col='3M'), size = 1) + 
        geom_line(aes(y=close_price$C, col='C'), size = 1) + 
        geom_line(aes(y=close_price$PG, col='PG'), size = 1) + 
        geom_line(aes(y=close_price$GOOG, col='GOOG'), size = 1) + 
        geom_line(aes(y=close_price$MYL, col='MYL'), size = 1) + 
        labs(x = "Time", y = "Daily closing price")
```

Discussion:
(Akmal)
<type here>

(Mark)
<type here>

(Sudheer)
<type here>

(Surya)

By looking at the daily closing price in 10 years from 2008 to 2018, I could see that the growth of the close price for GOOG (Alphabet Inc.) was positively growth over time. Initially, C (Citigroup Inc.) has a similar close price in 2008. However, their got a negative trend from early 2008 to mid 2008 which made them stuck for years ahead. Interestingly, even though the MMM (3M Company)'s performance was overshadowed with GOOG, they enjoyed quite a positive trend. The 3 others assets have a similar stagnant closing price over time.


Generate a time plot series of return series
```{r}
# View time plot of the 3M return price
 ggplot(data = transformed_data.returns, 
        aes(x=as.Date(returns$date), y=value, group=1) ) + 
        geom_line(aes(y=returns$MMM, col='3M'), size = 1, color='darkblue') + 
        labs(x = "Time", y = "Daily return series")

# View time plot of the C return price
 ggplot(data = transformed_data.returns, 
        aes(x=as.Date(returns$date), y=value, group=1) ) + 
        geom_line(aes(y=returns$C, col='C'), size = 1, color='darkred') + 
        labs(x = "Time", y = "Daily return series")

# View time plot of the GOOG return price
 ggplot(data = transformed_data.returns, 
        aes(x=as.Date(returns$date), y=value, group=1) ) + 
        geom_line(aes(y=returns$GOOG, col='GOOG'), size = 1, color='yellowgreen') + 
        labs(x = "Time", y = "Daily return series")

# View time plot of the MYL return price
 ggplot(data = transformed_data.returns, 
        aes(x=as.Date(returns$date), y=value, group=1) ) + 
        geom_line(aes(y=returns$MYL, col='MYL'), size = 1, color='deeppink') + 
        labs(x = "Time", y = "Daily return series")

# View time plot of the PG return price
 ggplot(data = transformed_data.returns, 
        aes(x=as.Date(returns$date), y=value, group=1) ) + 
        geom_line(aes(y=returns$PG, col='PG'), size = 1, color='blueviolet') + 
        labs(x = "Time", y = "Daily return series")
```

Discussion:
Similarities

The average value of all assets over 10 years was quite stable where the mean of log return is almost zero.

Difference
- MMM (Surya)

The average value of 3M asset over 10 years was quite stable where the mean of log return is almost zero. However, the volatility becomes larger for quite a long time at the end of 2008 and at the end of 2011; for a short time at the end of 2015 and mid 2017.

- C
<type here>

- GOOG
<type here>

- MYL
<type here>

- PG
<type here>

Generate a kernel density plot of return series
```{r}
library(kdensity)

# MMM
hist(transformed_data.returns$returns.MMM, breaks = 64, freq = FALSE, main = "3M Company", xlab = "Daily log returns")
kde_mmm = kdensity(transformed_data.returns$returns.MMM, start = "normal")
lines(kde_mmm, col="blue")
lines(kde_mmm, plot_start = TRUE, col="red")

# C
hist(transformed_data.returns$returns.C, breaks = 64, freq = FALSE, main = "Citigroup Inc.", xlab = "Daily log returns")
kde_c = kdensity(transformed_data.returns$returns.C, start = "normal")
lines(kde_c, col="blue")
lines(kde_c, plot_start = TRUE, col="red")

# PG
hist(transformed_data.returns$returns.PG, breaks = 64, freq = FALSE, main = "The Procter & Gamble Company", xlab = "Daily log returns")
kde_pg = kdensity(transformed_data.returns$returns.PG, start = "normal")
lines(kde_pg, col="blue")
lines(kde_pg, plot_start = TRUE, col="red")

# GOOG
hist(transformed_data.returns$returns.GOOG, breaks = 64, freq = FALSE, main = "Alphabet Inc.", xlab = "Daily log returns")
kde_goog = kdensity(transformed_data.returns$returns.GOOG, start = "normal")
lines(kde_goog, col="blue")
lines(kde_goog, plot_start = TRUE, col="red")

# MYL
hist(transformed_data.returns$returns.MYL, breaks = 64, freq = FALSE, main = "Mylan N.V.", xlab = "Daily log returns")
kde_myl = kdensity(transformed_data.returns$returns.MYL, start = "normal")
lines(kde_myl, col="blue")
lines(kde_myl, plot_start = TRUE, col="red")


```

Discussion:
Similarities
<type here>

Difference
- MMM (Surya)

There is a slight different in the left and left side which the density is quite lower than the right side. Thus, we could say that the data doesn't normally distributed. The kernel density has a higher kurtosis which result in much longer than normal tails of the density.

- C
<type here>

- GOOG
<type here>

- MYL
<type here>

- PG
<type here>

Generate a normal Q-Q plot of return series
```{r}
#MMM
mean_mmm = mean(transformed_data.returns$returns.MMM)
sd_mmm = sd(transformed_data.returns$returns.MMM)
mmm_std = (transformed_data.returns$returns.MMM - mean_mmm) / sd_mmm
qqnorm(mmm_std, main="3M Company Normal Q-Q Plot", plot.it = TRUE, datax = TRUE)
qqline(mmm_std, datax = FALSE, distribution = qnorm, probs = c(0.25, 0.75), qtype = 7)

#C
mean_c = mean(transformed_data.returns$returns.C)
sd_c = sd(transformed_data.returns$returns.C)
c_std = (transformed_data.returns$returns.C - mean_c) / sd_c
qqnorm(c_std, main="Citigroup Inc. Normal Q-Q Plot", plot.it = TRUE, datax = TRUE)
qqline(c_std, datax = FALSE, distribution = qnorm, probs = c(0.25, 0.75), qtype = 7)

#GOOG
mean_goog = mean(transformed_data.returns$returns.GOOG)
sd_goog = sd(transformed_data.returns$returns.GOOG)
goog_std = (transformed_data.returns$returns.GOOG - mean_goog) / sd_goog
qqnorm(goog_std, main="Alphabet Inc. Normal Q-Q Plot", plot.it = TRUE, datax = TRUE)
qqline(goog_std, datax = FALSE, distribution = qnorm, probs = c(0.25, 0.75), qtype = 7)

#MYL
mean_myl = mean(transformed_data.returns$returns.MYL)
sd_myl = sd(transformed_data.returns$returns.MYL)
myl_std = (transformed_data.returns$returns.MYL - mean_myl) / sd_myl
qqnorm(myl_std, main="Mylan N.V. Normal Q-Q Plot", plot.it = TRUE, datax = TRUE)
qqline(myl_std, datax = FALSE, distribution = qnorm, probs = c(0.25, 0.75), qtype = 7)

#PG
mean_pg = mean(transformed_data.returns$returns.PG)
sd_pg = sd(transformed_data.returns$returns.PG)
pg_std = (transformed_data.returns$returns.PG - mean_pg) / sd_pg
qqnorm(pg_std, main="The Procter & Gamble Company Normal Q-Q Plot", plot.it = TRUE, datax = TRUE)
qqline(pg_std, datax = FALSE, distribution = qnorm, probs = c(0.25, 0.75), qtype = 7)
```

Discussion:
Similarities
<type here>

Difference
- MMM (Surya)
The 3M asset has a thick tails which mean that, compared to the normal distribution, there is more data located at the extremes of the distribution and less data in the center of the distribution. In terms of quantiles this means that the first quantile is much less than the first theoretical quantile and the last quantile is greater than the last theoretical quantile.

- C
<type here>

- GOOG
<type here>

- MYL
<type here>

- PG
<type here>

Generate a scatter plot of return series for one asset againts the others
```{r}
ggplot(data = transformed_data.returns, aes(returns$MMM, (returns$C + returns$PG + returns$GOOG + returns$MYL))) +
  geom_point() + 
  labs(x = "3M Company", y = "Others")

ggplot(data = transformed_data.returns, aes(returns$C, (returns$MMM + returns$PG + returns$GOOG + returns$MYL))) +
  geom_point() + 
  labs(x = "Citigroup Inc.", y = "Others")

ggplot(data = transformed_data.returns, aes(returns$PG, (returns$MMM + returns$C + returns$GOOG + returns$MYL))) +
  geom_point() + 
  labs(x = "The Procter & Gamble Company", y = "Others")

ggplot(data = transformed_data.returns, aes(returns$GOOG, (returns$MMM + returns$C + returns$PG + returns$MYL))) +
  geom_point() + 
  labs(x = "Alphabet Inc.", y = "Others")

ggplot(data = transformed_data.returns, aes(returns$MYL, (returns$MMM + returns$C + returns$GOOG + returns$PG))) +
  geom_point() + 
  labs(x = "Mylan N.V.", y = "Others")

```

Compute the correlation matrix between all assets
```{r}
return_assets <- data.frame(transformed_data.returns$returns.MMM, transformed_data.returns$returns.C, transformed_data.returns$returns.GOOG, transformed_data.returns$returns.MYL, transformed_data.returns$returns.PG)

cor(return_assets)
```

Discussion:
Difference
- MMM (Surya)
Based on the result, the correlation between MMM with the others is quite small, which is either -0.01 or 0.01. Thus, I could conclude that MMM asset has quite a strong correlation with the other assets

- C
<type here>

- GOOG
<type here>

- MYL
<type here>

- PG
<type here>

SECTION 2 - UNIVARIATE TIME SERIES ANALYSIS

Load required libraries
```{r}
library(stats)
library(tseries)
library(forecast)
```

SECTION 2.1 - AUTOCORRELATION
Stationary analysis of the price series
```{r}
# MMM
mmm_percentage_change <- ts(transformed_data.close$close_price.MMM, frequency = 12, start = 2008)
mmm_percentage_change_truncated <- window(mmm_percentage_change, start = 2013)
acf(mmm_percentage_change)
acf(mmm_percentage_change_truncated)

# C
c_percentage_change <- ts(transformed_data.close$close_price.C, frequency = 12, start = 2008)
c_percentage_change_truncated <- window(c_percentage_change, start = 2013)
acf(c_percentage_change)
acf(c_percentage_change_truncated)

# PG
pg_percentage_change <- ts(transformed_data.close$close_price.PG, frequency = 12, start = 2008)
pg_percentage_change_truncated <- window(pg_percentage_change, start = 2013)
acf(pg_percentage_change)
acf(pg_percentage_change_truncated)

# GOOG
goog_percentage_change <- ts(transformed_data.close$close_price.GOOG, frequency = 12, start = 2008)
goog_percentage_change_truncated <- window(goog_percentage_change, start = 2013)
acf(goog_percentage_change)
acf(goog_percentage_change_truncated)

# MYL
myl_percentage_change <- ts(transformed_data.close$close_price.MYL, frequency = 12, start = 2008)
myl_percentage_change_truncated <- window(myl_percentage_change, start = 2013)
acf(myl_percentage_change)
acf(myl_percentage_change_truncated)
```

Discussion:
Similarities
<type here>

Difference
- MMM (Surya)

In this full autocorrelation, the spike was quite stable  on each lag, where it barely decreased. Because the spike has a value that is significantly different from zero, it becomes the evidence of autocorrelation. It also means when the close price of MMM stock rises, it tends to continue rising and vise versa. It also means that this is a non-stationary series because it is decaying.

The truncated autocorrelation also shows quite a similar result with the full autocorrelation which reinforced my argument that the MMM asset is quite stable over time.

- C
<type here>

- GOOG
<type here>

- MYL
<type here>

- PG
<type here>

Stationary analysis of the returns series
```{r}
# MMM
mmm_percentage_change <- ts(transformed_data.returns$returns.MMM, frequency = 12, start = 2008)
mmm_percentage_change_truncated <- window(mmm_percentage_change, start = 2013)
acf(mmm_percentage_change)
acf(mmm_percentage_change_truncated)

# C
c_percentage_change <- ts(transformed_data.returns$returns.C, frequency = 12, start = 2008)
c_percentage_change_truncated <- window(c_percentage_change, start = 2013)
acf(c_percentage_change)
acf(c_percentage_change_truncated)

# PG
pg_percentage_change <- ts(transformed_data.returns$returns.PG, frequency = 12, start = 2008)
pg_percentage_change_truncated <- window(pg_percentage_change, start = 2013)
acf(pg_percentage_change)
acf(pg_percentage_change_truncated)

# GOOG
goog_percentage_change <- ts(transformed_data.returns$returns.GOOG, frequency = 12, start = 2008)
goog_percentage_change_truncated <- window(goog_percentage_change, start = 2013)
acf(goog_percentage_change)
acf(goog_percentage_change_truncated)

# MYL
myl_percentage_change <- ts(transformed_data.returns$returns.MYL, frequency = 12, start = 2008)
myl_percentage_change_truncated <- window(myl_percentage_change, start = 2013)
acf(myl_percentage_change)
acf(myl_percentage_change_truncated)
```

Discussion:
Similarities
<type here>

Difference
- MMM (Surya)

Both full and truncated autocorrelation of 3M asset return price shows a similar result that there is a significant lag that we need to focus, especially on 0.1~0.2, 1.5, 1.9, and 2.9 because all of it was below the threshold. However, every lag is almost zero which we could interpret that there is no lag that influence the other lags that could give a significant spike.

- C
<type here>

- GOOG
<type here>

- MYL
<type here>

- PG
<type here>

Stationary analysis of the square of the returns series

```{r}
# MMM
mmm_percentage_change <- ts(transformed_data.returns$returns.MMM, frequency = 12, start = 2008)
mmm_percentage_change_truncated <- window(mmm_percentage_change, start = 2013)
acf(mmm_percentage_change^2)
acf(mmm_percentage_change_truncated^2)

# C
c_percentage_change <- ts(transformed_data.returns$returns.C, frequency = 12, start = 2008)
c_percentage_change_truncated <- window(c_percentage_change, start = 2013)
acf(c_percentage_change^2)
acf(c_percentage_change_truncated^2)

# PG
pg_percentage_change <- ts(transformed_data.returns$returns.PG, frequency = 12, start = 2008)
pg_percentage_change_truncated <- window(pg_percentage_change, start = 2013)
acf(pg_percentage_change^2)
acf(pg_percentage_change_truncated^2)

# GOOG
goog_percentage_change <- ts(transformed_data.returns$returns.GOOG, frequency = 12, start = 2008)
goog_percentage_change_truncated <- window(goog_percentage_change, start = 2013)
acf(goog_percentage_change^2)
acf(goog_percentage_change_truncated^2)

# MYL
myl_percentage_change <- ts(transformed_data.returns$returns.MYL, frequency = 12, start = 2008)
myl_percentage_change_truncated <- window(myl_percentage_change, start = 2013)
acf(myl_percentage_change^2)
acf(myl_percentage_change_truncated^2)
```

Discussion:
Similarities
<type here>

Difference
- MMM (Surya)

On the squared return of 3M asset squared return price, we could see that the progress of each lag was quite stable. There is no extreme increase nor decrease. I also could concluded that MMM stock didn't experience a significant increase or decrease of their price for quite a long time. It's positively stable.

- C
<type here>

- GOOG
<type here>

- MYL
<type here>

- PG
<type here>

SECTION 2.2 - PARTIAL AUTOCORRELATION
Stationary analysis of the price series
```{r}
# MMM
mmm_percentage_change <- ts(transformed_data.close$close_price.MMM, frequency = 12, start = 2008)
mmm_percentage_change_truncated <- window(mmm_percentage_change, start = 2013)
pacf(mmm_percentage_change)
pacf(mmm_percentage_change_truncated)

# C
c_percentage_change <- ts(transformed_data.close$close_price.C, frequency = 12, start = 2008)
c_percentage_change_truncated <- window(c_percentage_change, start = 2013)
pacf(c_percentage_change)
pacf(c_percentage_change_truncated)

# PG
pg_percentage_change <- ts(transformed_data.close$close_price.PG, frequency = 12, start = 2008)
pg_percentage_change_truncated <- window(pg_percentage_change, start = 2013)
pacf(pg_percentage_change)
pacf(pg_percentage_change_truncated)

# GOOG
goog_percentage_change <- ts(transformed_data.close$close_price.GOOG, frequency = 12, start = 2008)
goog_percentage_change_truncated <- window(goog_percentage_change, start = 2013)
pacf(goog_percentage_change)
pacf(goog_percentage_change_truncated)

# MYL
myl_percentage_change <- ts(transformed_data.close$close_price.MYL, frequency = 12, start = 2008)
myl_percentage_change_truncated <- window(myl_percentage_change, start = 2013)
pacf(myl_percentage_change)
pacf(myl_percentage_change_truncated)
```

Discussion:
Similarities
<type here>

Difference
- MMM (Surya)

Both full and truncated partial correlation of 3M asset close price shows that there is no lag that exceed the threshold and there is no strong impact from any lag. From here, we could say there this asset is quite stable-- there is no particular lag that could influence the other lags to get a significant spike.

- C
<type here>

- GOOG
<type here>

- MYL
<type here>

- PG
<type here>

Stationary analysis of the returns series
```{r}
# MMM
mmm_percentage_change <- ts(transformed_data.returns$returns.MMM, frequency = 12, start = 2008)
mmm_percentage_change_truncated <- window(mmm_percentage_change, start = 2013)
pacf(mmm_percentage_change)
pacf(mmm_percentage_change_truncated)

# C
c_percentage_change <- ts(transformed_data.returns$returns.C, frequency = 12, start = 2008)
c_percentage_change_truncated <- window(c_percentage_change, start = 2013)
pacf(c_percentage_change)
pacf(c_percentage_change_truncated)

# PG
pg_percentage_change <- ts(transformed_data.returns$returns.PG, frequency = 12, start = 2008)
pg_percentage_change_truncated <- window(pg_percentage_change, start = 2013)
pacf(pg_percentage_change)
pacf(pg_percentage_change_truncated)

# GOOG
goog_percentage_change <- ts(transformed_data.returns$returns.GOOG, frequency = 12, start = 2008)
goog_percentage_change_truncated <- window(goog_percentage_change, start = 2013)
pacf(goog_percentage_change)
pacf(goog_percentage_change_truncated)

# MYL
myl_percentage_change <- ts(transformed_data.returns$returns.MYL, frequency = 12, start = 2008)
myl_percentage_change_truncated <- window(myl_percentage_change, start = 2013)
pacf(myl_percentage_change)
pacf(myl_percentage_change_truncated)
```

Discussion:
Similarities
<type here>

Difference
- MMM (Surya)

Both full and truncated version show a similar result. Even though the graph shows a spiky lags, we need to focus on the y-range which is between -0.06~0.06. From here, we could say that all lags was almot zero barely significant. 

- C
<type here>

- GOOG
<type here>

- MYL
<type here>

- PG
<type here>

Stationary analysis of the square of the returns series
```{r}
# MMM
mmm_percentage_change <- ts(transformed_data.returns$returns.MMM, frequency = 12, start = 2008)
mmm_percentage_change_truncated <- window(mmm_percentage_change, start = 2013)
pacf(mmm_percentage_change^2)
pacf(mmm_percentage_change_truncated^2)

# C
c_percentage_change <- ts(transformed_data.returns$returns.C, frequency = 12, start = 2008)
c_percentage_change_truncated <- window(c_percentage_change, start = 2013)
pacf(c_percentage_change^2)
pacf(c_percentage_change_truncated^2)

# PG
pg_percentage_change <- ts(transformed_data.returns$returns.PG, frequency = 12, start = 2008)
pg_percentage_change_truncated <- window(pg_percentage_change, start = 2013)
pacf(pg_percentage_change^2)
pacf(pg_percentage_change_truncated^2)

# GOOG
goog_percentage_change <- ts(transformed_data.returns$returns.GOOG, frequency = 12, start = 2008)
goog_percentage_change_truncated <- window(goog_percentage_change, start = 2013)
pacf(goog_percentage_change^2)
pacf(goog_percentage_change_truncated^2)

# MYL
myl_percentage_change <- ts(transformed_data.returns$returns.MYL, frequency = 12, start = 2008)
myl_percentage_change_truncated <- window(myl_percentage_change, start = 2013)
pacf(myl_percentage_change^2)
pacf(myl_percentage_change_truncated^2)
```

Discussion:
Similarities
<type here>

Difference
- MMM (Surya)

Both full and truncated version shows a similar result. There are strong lags on the quarter half of the half which suddenly decrease and become stable after that.

- C
<type here>

- GOOG
<type here>

- MYL
<type here>

- PG
<type here>

SECTION 2.3 - ARIMA MODEL
Stationary analysis of the returns series
```{r}
# MMM
mmm_percentage_change <- ts(transformed_data.returns$returns.MMM, frequency = 12, start = 2008)
mmm_arma_model <- arma(window(mmm_percentage_change, start = 2008, end = 2018), order = c(12,0,0) )
summary(mmm_arma_model)
Box.test(mmm_arma_model$residuals, lag = 12)

# Citi
citi_percentage_change <- ts(transformed_data.returns$returns.C, frequency = 12, start = 2008)
citi_arma_model <- arma(window(citi_percentage_change, start = 2008, end = 2018), order = c(12,0,0) )
summary(citi_arma_model)
Box.test(citi_arma_model$residuals, lag = 12)

# P & G
pg_percentage_change <- ts(transformed_data.returns$returns.PG, frequency = 12, start = 2008)
pg_arma_model <- arma(window(pg_percentage_change, start = 2008, end = 2018), order = c(12,0,0) )
summary(pg_arma_model)
Box.test(pg_arma_model$residuals, lag = 12)

# Google
goog_percentage_change <- ts(transformed_data.returns$returns.GOOG, frequency = 12, start = 2008)
goog_arma_model <- arma(window(goog_percentage_change, start = 2008, end = 2018), order = c(12,0,0) )
summary(goog_arma_model)
Box.test(goog_arma_model$residuals, lag = 12)

# MYL
myl_percentage_change <- ts(transformed_data.returns$returns.MYL, frequency = 12, start = 2008)
myl_arma_model <- arma(window(myl_percentage_change, start = 2008, end = 2018), order = c(12,0,0) )
summary(myl_arma_model)
Box.test(myl_arma_model$residuals, lag = 12)
```

Discussion:
- MMM (Surya)
<type here>

Stationary analysis of the square of the returns series
```{r}
#MMM
mmm_percentage_change <- ts(transformed_data.returns$returns.MMM^2, frequency = 12, start = 2008)
mmm_arma_model <- arma(window(mmm_percentage_change, start = 2008, end = 2018), order = c(12,0,0) )
summary(mmm_arma_model)
Box.test(mmm_arma_model$residuals, lag = 12)

# Citi
citi_percentage_change <- ts(transformed_data.returns$returns.C^2, frequency = 12, start = 2008)
citi_arma_model <- arma(window(citi_percentage_change, start = 2008, end = 2018), order = c(12,0,0) )
summary(citi_arma_model)
Box.test(citi_arma_model$residuals, lag = 12)

# P & G
pg_percentage_change <- ts(transformed_data.returns$returns.PG^2, frequency = 12, start = 2008)
pg_arma_model <- arma(window(pg_percentage_change, start = 2008, end = 2018), order = c(12,0,0) )
summary(pg_arma_model)
Box.test(pg_arma_model$residuals, lag = 12)

# Google
goog_percentage_change <- ts(transformed_data.returns$returns.GOOG^2, frequency = 12, start = 2008)
goog_arma_model <- arma(window(goog_percentage_change, start = 2008, end = 2018), order = c(12,0,0) )
summary(goog_arma_model)
Box.test(goog_arma_model$residuals, lag = 12)

# MYL
myl_percentage_change <- ts(transformed_data.returns$returns.MYL^2, frequency = 12, start = 2008)
myl_arma_model <- arma(window(myl_percentage_change, start = 2008, end = 2018), order = c(12,0,0) )
summary(myl_arma_model)
Box.test(myl_arma_model$residuals, lag = 12)
```

Discussion:
- MMM (Surya)
<type here>