---
title: "3M - 10 Years of Historical Price 01/09/2008 ~ 01/09/2018"
output: html_notebook
---

SECTION 0 - OBTAIN AND TRANSFORMING DATA

3M CSV dataset

```{r}
dataset_MMM <- read.csv("MMM.csv")
head(dataset_MMM)
summary(dataset_MMM)
```

C CSV dataset
```{r}
dataset_C <- read.csv("C.csv")
head(dataset_C)
summary(dataset_C)
```

PG CSV dataset
```{r}
dataset_PG <- read.csv("PG.csv")
head(dataset_PG)
summary(dataset_PG)
```

GOOG CSV dataset
```{r}
dataset_GOOG <- read.csv("GOOG.csv")
head(dataset_GOOG)
summary(dataset_GOOG)
```

MYL CSV dataset
```{r}
dataset_MYL <- read.csv("MYL.csv")
head(dataset_MYL)
summary(dataset_MYL)
```


Retrieve the daily closing price
```{r}
# Initialize date column for analyze purpose
# close_price$date = dataset_MMM$Date

close_price$MMM = dataset_MMM$Close
close_price$C = dataset_C$Close
close_price$PG = dataset_PG$Close
close_price$GOOG = dataset_GOOG$Close
close_price$MYL = dataset_MYL$Close

#Show several example of each asset's close price
head(close_price$MMM)
head(close_price$C)
head(close_price$PG)
head(close_price$GOOG)
head(close_price$MYL)
```

Construct the log daily returns of each asset
```{r}
# Initialize date column for analyze purpose
returns$MMM = diff(log(close_price$MMM), lag = 1)
returns$C = diff(log(close_price$C), lag = 1)
returns$PG = diff(log(close_price$PG), lag = 1)
returns$GOOG = diff(log(close_price$GOOG), lag = 1)
returns$MYL = diff(log(close_price$MYL), lag = 1)

#Show several example of each asset's close price
head(returns$MMM)
head(returns$C)
head(returns$PG)
head(returns$GOOG)
head(returns$MYL)
```

Insert the result into data frame format
```{r}
transformed_data.close <- data.frame(close_price$date, close_price$MMM, close_price$C, close_price$PG, close_price$GOOG, close_price$MYL)
str(transformed_data.close)

n <- nrow(transformed_data.close)

returns$date <- returns$date[2:n]

transformed_data.returns <- data.frame(returns$date, returns$MMM, returns$C, returns$PG, returns$GOOG, returns$MYL)
str(transformed_data.returns)
```


SECTION 1 - EXPLORATORY DATA ANALYSIS

Generate a time plot series of closing price on the same graph
```{r}
# Load necessary packages
library(tidyverse)
library(ggplot2)


# View time plot of the closing price
 ggplot(data = transformed_data.close, 
        aes(x=as.Date(close_price$date), y=value, group=1) ) + 
        geom_line(aes(y=close_price$MMM, col='3M'), size = 1) + 
        geom_line(aes(y=close_price$C, col='C'), size = 1) + 
        geom_line(aes(y=close_price$PG, col='PG'), size = 1) + 
        geom_line(aes(y=close_price$GOOG, col='GOOG'), size = 1) + 
        geom_line(aes(y=close_price$MYL, col='MYL'), size = 1) + 
        labs(x = "Time", y = "Daily closing price")
```

Discussion:
(Surya)
By looking at the daily closing price in 10 years from 2008 to 2018, I could see that the growth of the close price for GOOG (Alphabet Inc.) was positively growth over time. Initially, C (Citigroup Inc.) has a similar close price in 2008. However, their got a negative trend from early 2008 to mid 2008 which made them stuck for years ahead. Interestingly, even though the MMM (3M Company)'s performance was overshadowed with GOOG, they enjoyed quite a positive trend. The 3 others assets have a similar stagnant closing price over time.

Generate a time plot series of return series on the same graph
```{r}

# View time plot of the closing price
 ggplot(data = transformed_data.returns, 
        aes(x=as.Date(returns$date), y=value, group=1) ) + 
        geom_line(aes(y=returns$MMM, col='3M'), size = 1) + 
        labs(x = "Time", y = "Daily return series")
```

Discussion:
(Surya)

The average value of 3M asset over 10 years was quite stable where the mean of log return is almost zero. However, the volatility becomes larger for quite a long time at the end of 2008 and at the end of 2011; for a short time at the end of 2015 and mid 2017.